\chapter{Program Creation} % (fold)
\label{cha:program_creation}

\begin{quote}
  \Fontlukas\Large
  \renewcommand{\LettrineTextFont}{\relax}
  \lettrine[image=true,lines=3,lraise=0.1]
  {C}{asting} spells crafted by others is alright, but the true power of magic can only be realised by crafting your own spells. You have done well mastering the tools, so now let us turn our attention to the study of the arcane knowledge of spell craft. To create your own spells you need to know\ldots
\end{quote}

\bigskip

Compiling programs crafted by others is alright, but the true power of programming can only be realised by learning to craft your own programs. \cref{cha:building programs} introduced you to the tools you need to compile programs from source code, so now we can turn our attention to the study program creation.

This chapter introduces the artefacts used to create programs, and how you can code these using a programming language. You will start by learning to create simple programs that output information to the Terminal, and then we will look at making use of SplashKit to create some more interesting programs.

When you have understood the material in this chapter you will be able to write the code needed to declare a program, and within this program create your own custom procedures to perform simple tasks. You will be able to convert this code into an executable file using a compiler, and then run the program you created. You will have made those first important steps in your journey to master this arcane knowledge. 

\minitoc

\input{topics/program-creation/concepts/program-creation-concepts}

% ======================
% = Using the Concepts =
% ======================

\clearpage
\section{Using these Concepts} % (fold)
\label{sec:using_these_concepts_program_creation}

Armed with the knowledge you have gained in the Section \ref{sec:program_creation_concepts} you can now start to make your own small program.

\input{topics/program-creation/application/design-hello-world}

% section using_these_concepts (end)



\input{topics/program-creation/c/program-creation-in-c}
\input{topics/program-creation/pascal/program-creation-in-pascal}


% =========================
% = Visualising Execution =
% =========================
\cleardoublepage
\def\pageLang{none}
\section{Understanding Program Execution} % (fold)
\label{sec:understanding_program_execution}

\input{topics/program-creation/application/visualise-hello-world}

% section understanding_program_execution (end)

% ====================
% = Examples Section =
% ====================
\clearpage
\section{Program Creation Examples} % (fold)
\label{sec:program_creation_examples}

\input{topics/program-creation/examples/program-creation-examples}

% section program_creation_examples (end)

% =============
% = Exercises =
% =============
\clearpage
\section{Program Creation Exercises} % (fold)
\label{sec:program_creation_exercises}

\input{topics/program-creation/exercises/exercises}

% section program_creation_exercises (end)

% ===================
% = Project Section =
% ===================
% \clearpage
% \section{Program Creation Project} % (fold)
% \label{sec:program_creation_project}
% 
% section program_creation_project (end)

% chapter program_creation (end)