\clearpage
\section{Input and Output Exercises} % (fold)
\label{sec:input_and_output_exercises}

\subsection{Concept Questions} % (fold)
\label{sub:file-io-concept_questions}

\begin{enumerate}
  \item Why would you want to save data to file?
  \item What are the basic operations that you can perform with files?
  \item What is the difference between a text file and a binary file? Explain. 
  \item What challenges to saving variable sized data to file raise? How can these be addressed?
  \item How is reading and writing to files similar to working with the Terminal?
\end{enumerate}

% subsection concept_questions (end)

\subsection{Code Writing Questions: Applying what you have learnt} % (fold)
\label{sub:code_writing_questions_applying_what_you_have_learnt}

\begin{enumerate}
  \item Write two programs that save three integer values to file, one that saves it to a text file the other to a binary file. Execute the two programs and compare the files created.
  \item Write two programs that read three integer values from file, one that reads them from a text file the other from a binary file. Once the data is loaded into memory have the program output them to the terminal.
  \item Use the code from this chapter to implement saving data for the Small DB program.
  \item Revisit your statistics programs and have it save the values the user enters to file when the programs ends. Once this is working add the code to load the data from the file when the programs starts.
\end{enumerate}

% subsection code_writing_questions_applying_what_you_have_learnt (end)

\subsection{Extension Questions} % (fold)
\label{sub:extension_questions}

\begin{enumerate}
  \item Explore the other file IO functions and procedures offered by the language you are using. See if you can work out how to move the cursor within the file (seek to a new location). Use this to move back and forth within a file reading individual values in response to user input. 
\end{enumerate}

% subsection extension_questions (end)

% section input_and_output_exercises (end)
