\clearpage
\section{Pascal Program} % (fold)
\label{sec:pascal-basic-program}

Pascal includes syntax to allow you to declare a program in your code. The code for a Pascal program is written

Your program contains the instructions that are followed when the user runs the executable file. In many cases you will want to use code from other \nameref{sec:unit}s. This is achieved using the uses clause. By default all program's have access to the \texttt{System} unit, which contains \nameref{sec:writeln} and many other useful procedures.

\subsection*{Pascal Syntax} % (fold)
\label{sub:programsgeneralform}

\input{syntax-out/pascal/program-creation/program}
% subsection general_form (end)

\subsection*{Example} % (fold)
\label{sub:programExamples}

The code in Listing \ref{lst:pascal-program-creation-HelloWorld} and Listing \ref{lst:pascal-program-creation-ClrScr} show two example programs. Listing \ref{lst:pascal-program-creation-HelloWorld} contains the instructions that for a program which greets the world when it is executed, printing the text \emph{Hello World} to the Terminal. The program in Listing \ref{lst:pascal-program-creation-ClrScr} shows how to use code from the CRT \nameref{sec:unit}, the code for the \texttt{ClrScr} procedure is contained in the \texttt{CRT} Unit.

\lstinputlisting[caption={The classic ``Hello World'' program.},label={lst:pascal-program-creation-HelloWorld}]{./topics/program-creation/pascal/HelloWorld.pas}
\lstinputlisting[caption={Example of unit use, using the \texttt{CRT} unit},label={lst:pascal-program-creation-ClrScr}]{code/pascal/program-creation/ClearScreen.pas}

% subsection program_examples (end)

\mynote{
\begin{itemize}
    \item The program in Listing~\ref{lst:HelloWorld} is named `HelloWorld', see \nameref{sec:identifier}.
    \item A program's instructions start at the \texttt{begin} \nameref{sec:keyword}.
    \item The `Hello World' program in Listing~\ref{lst:HelloWorld} has one statement that uses \nameref{sec:writeln}.
    \item The statements are grouped within a \emph{block} that ends with the \texttt{end} \nameref{sec:keyword}.
    \item Program's end at the full stop (at \texttt{end.}).
    \item \nameref{sec:writeln} comes from the System unit, to use code in other units you need to include the uses clause.
\end{itemize}
}
% subsection program_study (end)

% section program (end)