\chapter*{Preface} % (fold)
\label{cha:preface}

\begin{quote}
  %\frakfamily\selectfont\Large
  \Fontlukas\Large
  \renewcommand{\LettrineTextFont}{\relax}
  \lettrine[image=true,lines=3,lraise=0.1]
  {W}{elcome} neophyte!  So you seek to master the arts of Magic. Well, you have come to the right place. Here we will give you the opportunity to explore magic, to understand its working and use. Before we start I have one piece of advice for you, practice, for it is only through practice that you can hope to learn these secret arts.
\end{quote}

\bigskip

Welcome to the Programming Arcana\footnote{Arcana is defined as secrets or mysteries, Wiktionary defines it as ``specialized knowledge that is mysterious to the uninitiated.''. This fits well with the idea of programming, and we think it is a cool word to describe the \emph{magic} of programming!}, a book about learning to program. This book contains a number of chapters that take you from knowing nothing, or little, about programming to a position where the mysteries are revealed. By the end of the material you will be able to create your own programs and you will be ready to start learning other programming languages and approaches to software development.

This book is divided into a number of chapters, each of which introduces you to a programming task and the arcane knowledge that must be attained to understand how the task is accomplished. As with any arcane knowledge there are special terms that are used by those who know its secrets. In each chapter you will be introduced to the terms you need to understand in order to perform the current task. This will provide you with the tools you need to describe programs to other software developers, and will help you understand how the structures within your programs work to achieve their goals.

Before we start getting into details let us have a look at how you can use this book to help you become a master of the arcane arts of programming.

\input{topics/preface/BookOverview}
\input{topics/preface/ConceptTaxonomy}

\section*{Advice} % (fold)
\label{sec:advice}

If you want, or need, to learn to program then you can not do this just by reading a book, even one as magical as this. Learning to program requires practice. This book is designed to give you the concepts you need in order to understand how to go about creating your first programs. To really understand these concepts you need to apply them to the creation of your own programs.

When you are getting started, programming can appear quite daunting and the tools you use can be unforgiving. Work through these initial challenges, and with practice you will be able to overcome them. Once you have some success there is nothing better than seeing a program you created running on a computer. You have brought the machine to life, getting it to perform a task the way you want it performed. Once you get a program working it can become easy to get hooked and working on new features and functions becomes a real joy. The greater the challenge the program offers, the greater your sense of achievement when you see the working product in operation.

Other people are the best resources to help you get over these initial challenges. Fellow students studying this material can provide you with support, and a chance to discuss the challenges you are facing. Teaching staff are also a good resource when you are really stuck. If you do not have access to anyone who can help, use discussion boards and websites. Getting the right help will make a large difference to your learning experience.

Remember that you will need to study this material. That is not just reading it, but thinking and reflecting on what you have read. Try to think about each of the concepts, and how they relate to the other material that has been presented to you. Try to design and build your own programs with the material you are learning. If you do think deeply and apply the concepts to programs you create, you will eventually get the light bulb moment when things become clear and programming can become truly joyful.

% section advice (end)

% chapter preface (end)