\chapter{Procedure Declaration} % (fold)
\label{cha:procedure_declaration}

\begin{quote}
  \Fontlukas\Large
  \renewcommand{\LettrineTextFont}{\relax}
  \lettrine[image=true,lines=3,lraise=0.1]
  {Y}{our} spell casting is really coming along. As you know, your spells contain a sequence of incantations. I will now teach you a technique to combine incantations into groups. This will make your spells faster to cast, and easier to use. Now get your wand, and try casting your spell like this\ldots
\end{quote}

\bigskip

Programs contain a sequence of instructions, with each instruction \emph{commanding} the computer to perform an action. While it is possible to have just a single long list of instructions, this quickly becomes difficult to understand, hard to extend, and frustrating to maintain. Rather than coding all of a program's instructions in a single list, Software Developers arrange a program's instructions in meaningful groups that can be called when those steps need to be performed. These groups are called \emph{Procedures}. Within a Program, each Procedure is designed to get the computer to perform a single task, and therefore only contains the instructions related to that task.

When you have understood the material in this chapter you will be able to create and call simple Procedures of your own creation. This will help make your programs faster and easier to write.

\minitoc

% ====================
% = Concepts Section =
% ====================

\input{topics/program-decl/concepts/procedure-decl-concepts}

% ========================
% = Using these concepts =
% ========================

\clearpage
\section{Using these Concepts} % (fold)
\label{sec:using_these_concepts_procedure_decl}

Procedures give us a means of modelling the tasks we want the computer to perform. Rather than just having a long list of instructions, we can create procedures that contain the steps needed to perform individual tasks that the program must carry out. The program's instructions can then be very simple, just calling the procedures that we have written to carry out the tasks as needed.

\input{topics/program-decl/application/design-morse-calling}


% section using_these_concepts (end)

% =============
% = C Section =
% =============

\input{topics/program-decl/c/procedure-decl-in-c}

% ==================
% = Pascal Section =
% ==================

\input{topics/program-decl/pascal/procedure-decl-in-pascal}

% =========================
% = Understanding Section =
% =========================
\clearpage
\def\pageLang{none}
\section{Understanding Procedure Declaration and Calls} % (fold)
\label{sec:understanding_procedure_declaration_and_calls}

\input{topics/program-decl/application/visualise-procedures}

% section understanding_procedure_declaration_and_calls (end)

% ====================
% = Examples Section =
% ====================
\clearpage
\section{Procedure Declaration Examples} % (fold)
\label{sec:procedure_declaration_examples}

\input{topics/program-decl/examples/procedure-decl-examples}

% section procedure_declaration_examples (end)

% =============
% = Exercises =
% =============
\clearpage
\section{Procedure Declaration Exercises} % (fold)
\label{sec:procedure_declaration_exercises}

\input{topics/program-decl/exercises/procedure-decl-exercises}

% section procedure_declaration_exercises (end)

% ===================
% = Project Section =
% ===================
% \clearpage
% \section{Procedure Declaration Project} % (fold)
% \label{sec:procedure_declaration_project}



% section procedure_declaration_project (end)
% chapter procedure_declaration (end)