\clearpage
\subsection{Challenges and Rewards} % (fold)
\label{sub:challenges_and_rewards}

% subsection challenges_and_rewards (end)

Programming in a third generation language, like C++ and Pascal, requires you to master several different things, as shown in the following list. The following chapters will work on building your knowledge and skills in each of these aspects.

\begin{enumerate}
  \item What is it that you want the program to do? Writing a program is like writing instructions for someone to carry out. If you do not know how to perform the task yourself you will not be able to tell someone else how to perform the task.
  \item You need to understand what the computer is capable of doing. Computers are unintelligent, so writing a program is more challenging than giving instructions to a person as the computer cannot interpret what you mean and will follow your instructions to the letter, regardless of the effect. The capabilities of the computer limit the flexibility you have for expressing your solution.
  \item The language you choose to develop with also limits how you express your solution. You need to understand the artefacts that you can create, how these artefacts are written in source code, and how these are executed by the computer.
  \item Finally you need to understand how to locate and correct issues with your programs. This includes responding to syntax errors reported to you by the compiler, as well being able to locate errors where the program does not operate the way you intended. 
\end{enumerate}

\emph{With all of these challenges, what appeal does software development have?}

There is nothing better than seeing a program you created running on a computer. You have brought the machine to life, getting it to perform a task the way you want it performed. Once you get a program working it can become easy to get hooked and working on new features and functions becomes a real joy. The greater the challenge the program offers, the greater your sense of achievement when you see the working product in operation.

% subsection compiling_code (end)