% \begin{savequote}[10pc]
% \sffamily
% Smoke whirls\\
% After the passage of a train.\\
% Young foliage.
% \qauthor{Shiki Masaoka (1867-1902)}
% \end{savequote}

\chapter{Program Creation} % (fold)
\label{cha:programCreation}

\begin{quote}
  %\frakfamily\selectfont\Large
  \Fontlukas\Large
  \renewcommand{\LettrineTextFont}{\relax}
  \renewcommand{\LettrineFontHook}{\color{red}}
  \lettrine[image=true,lines=3,lhang=.2, loversize=.25, findent=0.1em]
  {W}{elcome} neophyte! So you seek to master the art of Magic? To work magic you must learn the structure of incantations, and how to use a wand to convert these into magic energy. 
  
  Let us begin with a simple spell, a spell that will greet the world around you! Utter these words, and wave your wand\ldots
\end{quote}

\bigskip

Welcome to the Programming Arcana\footnote{Arcana is defined as secrets or mysteries, Wiktionary defines it as ``specialized knowledge that is mysterious to the uninitiated.''. This fits well with the idea of programming, and we just think its a cool word to describe the \emph{magic} of programming!}, a book about learning to program. This book contains a number of lessons that take you from knowing nothing, or little, about programming to a position where the mysteries are revealed. By the end of the material you will be able to create your own programs and you will be ready to start learning other programming languages and approaches to software development.

This book is divided into a number of chapters, each of which introduces you to a programming task and the arcane knowledge that must be attained to understand how the task is accomplished. As with any arcane knowledge there are special terms that are used by those who know its secrets. In each chapter you will be introduced to the terms you need to understand in order to perform the current task. This will provide you with the tools you need to describe programs to other software developers, and will help you understand how the structures within your programs work to achieve their goals.

Like magic, you must learn the structure of source code, and how to use tools to convert these into executable programs. Let us begin with a simple program, a program that will greet the world.

\clearpage

\input{concepts/compilers/compilers}

\input{topics/program-creation/pascal/pascal-basic-program.tex}

% chapter program_creation (end)