\chapter{Control Flow} % (fold)
\label{cha:control_flow}

\begin{quote}
  \Fontlukas\Large
  \renewcommand{\LettrineTextFont}{\relax}
  \lettrine[image=true,lines=3,lraise=0.1]
  {T}{ime} has come for you to learn how to control the flow of the magical energies. This arcane knowledge will unlock great power. Making it possible to do things that until now seemed impossible. Close your eyes and picture the energy travelling through your spell. Take control of that flow by\ldots
\end{quote}

\bigskip


The focus so far has been on learning the programming artefacts that you can create within your code. You have seen how to create \nameref{sub:program}s, \nameref{sub:procedure}s, \nameref{sub:function}s, and \nameref{sub:variable}s. The actual instructions that you can issue to the computer have been limited to \nameref{sub:procedure call}s, \nameref{sub:function_call}s, and \nameref{sub:assignment_statement}s. This Chapter will introduce you to the other actions that you can command the computer to perform. It will show you how to control the flow of the instructions, unlocking great power, and making it possible to do things that until now seemed impossible.

When you have understood the material in this chapter you will be able to write code that commands the computer to perform a wider range of actions by controlling the sequence in which the basic commands are performed.

\minitoc

% ============
% = Concepts =
% ============
\input{topics/control-flow/concepts/control-flow-concepts}

% ======================
% = Using Control Flow =
% ======================
\clearpage
\section{Using these Concepts} % (fold)
\label{sec:control_flow_using_these_concepts}

The Control Flow Statements enable you to alter the purely sequential order in which instructions are performed. Using these Statements you can have the computer select a path to follow, or jump back and repeat statements a number of times. These capabilities make it possible to create programs that react to the data they receive, giving more interactive results than were possible before.

\input{topics/control-flow/application/using-control-flow}

% section using_these_concepts (end)

% =============
% = C Section =
% =============
\input{topics/control-flow/c/control-flow-in-c}

% ==================
% = Pascal Section =
% ==================
\input{topics/control-flow/pascal/control-flow-in-pascal}

% ===========================
% = Understanding Data Flow =
% ===========================

\clearpage
\def\pageLang{None}
\section{Understanding Control Flow} % (fold)
\label{sec:understanding_control_flow}

\input{topics/control-flow/understanding/understanding-control-flow}

% section understanding_control_flow (end)

% ====================
% = Examples Section =
% ====================
\clearpage
\section{Control Flow Examples} % (fold)
\label{sec:control_flow_examples}

\input{topics/control-flow/examples/examples-flow}

% section control_flow_examples (end)

% =============
% = Exercises =
% =============
\clearpage
\section{Control Flow Exercises} % (fold)
\label{sec:control_flow_exercises}

\input{topics/control-flow/exercises/exercises-flow}

% section control_flow_exercises (end)

% ===========
% = Project =
% ===========
% \clearpage
% \section{Control Flow in the Project} % (fold)
% \label{sec:control_flow_in_the_project}

% section control_flow_in_the_project (end)

% chapter control-flow (end)